---
title: "Fars Functions"
author: "Federica Bisio"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The functions provided use data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

## Functions Info

The functions provide several methods to read and summarize the above data, divided by years.

## How to use the functions

Create the file name starting from the year:
```{r, eval=FALSE}
make_filename(year=2014)
```

Read a csv file and transform it into a table:
```{r, eval=FALSE}
f<-fars_read(filename)
```

Create a list of tables corrisponding to different years:
```{r, eval=FALSE}
fars_read_years(years=c(2014,2015))
```

Summarize results from multiple years:
```{r, eval=FALSE}
fars_summarize_years(years=c(2014,2015))
```



## Figures

Create a graph for a specific state and year:

```{r,fig.show='hold',warning=FALSE,message=FALSE}
library(maps)
library(farspackage)
fars_map_state(state.num=1,year=2014)
```

